%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}


\begin{document}
\header{Ritwik}{Sharma}
       {Computer Science Undergraduate}
       
       
\begin{tabular}{c|c|c|c}
    {\faMobile\ \@(+91) 8126445890}\hspace{.5cm}  &\hspace{.5cm}   
    \href{mailto:ritwik.1204@gmail.com}{\faEnvelope\ \@ritwik.1204@gmail.com} \hspace{.5cm} & \hspace{.5cm}
    \href{https://github.com/ritwik12}{\faGithubSquare\ \@ritwik12} \hspace{.5cm} & \hspace{.5cm}
    \href{https://ritwik12.github.io}{\faHome\ \@ritwiksharma}
    \hspace{.5cm}
    
    
     
\end{tabular}


\section{Education}

\begin{entrylist}
  \entry
    {2015-2019}
    {B.Tech. {\normalfont Computer Science \& Engineering}}
    {UPES, Dehradun}
    {\emph{Specialization in Open Source \& Open Standards}}
    
\end{entrylist}

\section{Experience}

\begin{entrylist}
  \entry
    {May 2017 to July 2017}
    {Hackr.io}
    {Work from Home}
    {{Joined as Social media Marketer and Programmer}
    
    {Promoted to Associate Manager, leader of a 6 members team}
    
    {Promoted to Project Manager, managed a group of 100 interns}
    
    \emph{Programming Internship}
    
    {
    {\normalfont  - Designed Front-end prototype for Hackr.io website \href{https://ritwik12.github.io/Prototype-For-Hackr.io/}{(\textbf {Prototype For Hackr.io})}}}
    
    {\normalfont  - Technology used: HTML, CSS, JavaScript, Bootstrap}
    
    \emph{Marketing Internship}
    
     {\normalfont  - Worked as social media marketer and managed a Facebook group of 900 members.}
     
     {\normalfont  - Worked on Quora and answered Technical questions.}
     
    }
\end{entrylist}

\section{Honors \& Awards}

\begin{entrylist}
  \entry
    {}
    {International rank 274, \normalfont National Science Olympiad (NSO) organized by SOF.}
    {}
    {}
  \entry
    {March 2017}
    {DART AND DASH}
    {Digital India Week}
    {Secured 1st rank with cash prize among various coders in coding event "DART AND DASH" held at University Of Petroleum And Energy Studies.}
  \entry
    {March 2017}
    {MINDSWEEPER}
    {IIT Roorkee}
    {Secured 5th rank in a coding event "MINDSWEEPER" on "Hackerrank" organized at IIT roorkee during Cognizance 2017.}
    
\end{entrylist}

\section{Projects}
\begin{entrylist}
  \entry
    {Ongoing}
    {intelligent Personal Assistant}
    {Minor 1}
    {A virtual assistant based on Artificial Intelligence that can perform tasks or services for an individual. }  
\end{entrylist}

\section{Skills}
    
    \textbf{Programming}  
    \emph{\hspace{0.5cm}Proficient:} C/C++ \emph{\hspace{0.5cm} Experienced:} Java, C\# \\ 
    \textbf{\hspace{1.45cm} Web} 
    \hspace{0.4cm} PHP, JavaScript, Bootstrap, HTML, CSS  \\
    \textbf{\hspace{0.9cm} Utilities} 
    \hspace{0.4cm} Linux shell utilities, Git, \LaTeX

    
\section{Extracurricular Activity}
\begin{entrylist}
  \entry
    {2015}
    {Yugmak}
    {Computer Society Of India}
    {Event organizer at Yugmak (a national event organized by CSI).}
    
  \entry
    {2017}
    {Cognizance}
    {IIT Roorkee}
    {Campus Ambassador at UPES Dehradun for Cognizance IIT roorkee (Techfest) 2017 under Student Partnership Programme.}
    
  \entry
    {2015-2016}
    {Computer Society Of India}
    {}
    {Core Committee member of Computer Society Of India (CSI)}
    
  
\end{entrylist}


\section{Coursework}
\begin{flushleft}
    Design and Analysis of Algorithms   \hspace{3cm} 
    Operating Systems\\ 
    Software Engineering \& Project Mgmt \hspace{2.45cm} Computer System Architecture \\  
    IT Applications and Open Standards \hspace{2.67cm} Web Technologies through PHP \\
    Data Communication and Computer Networks \hspace{1.15cm} Administering Open Source Systems

\end{flushleft}
 
\section{Miscellaneous}
\begin{itemize}
    \item Contribute to open source, \href{https://github.com/ritwik12}{Github}
\end{itemize}


 













%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
